\plaintitle

### 2016-06-15 chi/papers/2017/referrals/referrals.tex
total rewrite of the tracking labor intro

Hi there.
\section{Introduction}
The practice of referring work to other skilled workers has been well--studied in economics and more broadly in the social sciences for decades
[\textit{citation needed}].
But researchers in crowd work haven't sufficiently explored the potential
to employ this characteristic of socially connected workers
to give professionals opportunities to better route tasks.
One possible reason for this may have been the assumption that workers are not necessarily well--connected.
This would be an intuitively reasonable assumption
--- with no in--built forums or communities for workers on various gig labor markets
(e.g. Uber, Amazon Mechanical Turk (AMT), etc\dots),
one might reasonably conclude that these workers are not collaborative.

But, as
\citeauthor{crowdcollab} identifies,
crowd workers are substantially more collaborative than we originally may have inferred
\cite{crowdcollab}.
Given this realization, we pose the question:
can requesters operationalize this finding to get work done more effectively than conventional methods would allow?
Perhaps more importantly, can employing this finding allow workers
to contribute meaningfully to tasks
in ways that do not necessarily fall under the existing paradigms
(e.g. ``find--fix--verify'')
\cite{bernstein2015soylent}?

>>>>

\itshape
Sample intro. Does this sell the idea?
\upshape

\section{Introduction}

### 2016-06-15 cscw/papers/2017/labor/trackingWork.tex
total rewrite of the tracking labor intro

\section{Introduction}
The past decade has seen
paid microtasking, the ``sharing economy'', and other instantiations of on--demand contract work
grow to occupy the fascination of both academic circles and our culture as a whole
\cite{Ross,CrowdsourcingUserStudies,scholz2012digital}.
The research community has made connections between this emergent form of work
and the historically situated ``piecework'',
as well as a number of observations relating to
the frustration workers feel stemming from the management of this work,
but situating the causes of these frustrations either in the larger body of scholarship on crowd work,
or crowd work itself,
has proven difficult;
the connection between crowd work and a historical parallel contextualizing its ongoing developments 
hasn't been deeply made yet
\cite{turkopticon,dynamo,uberAlgorithm}.

While much of this work appears to gesture toward
the parallels between contemporary on--demand work and piecework,
it's proven difficult to bring the totality of these observations into focus using one theoretical lens.
This paper will attempt to do so by arguing that
the topics social computing researchers have investigated are
not just parallel to historical piecework and
the process of factorization that took place in the early \nth{20} century;
indeed, these phenomena \textit{precipitate and reinforce each other}.

In the reflection on the literature published in the last 5 years since
\citeauthor{crowdworkFuture}'s 
\citetitle{crowdworkFuture},
we notice a broader trend describing the change in work that's being done
\cite{crowdworkFuture}.
Following the improvements in
breaking down tasks,
delegating work, and
managing workers more broadly,
crowd--powered work has continued to parallel historical piecework's trajectory
by outgrowing ad--hoc worker groups and coalescing into more formal working groups,
for example through the use of a ``white list'' of familiar workers.
We might call this the regularization of factory work.

Making sense of the broader field of crowd work
by looking at the movements toward
distributing work,
routinizing and breaking down tasks,
and externally managing workers
as linked to one another, 
we give ourselves a framing of contemporary piecework that explains,
and arguably predicts,
what we have seen thus far
--- and perhaps what we should expect to see going forward.

This paper will attempt to demonstrate that the familiarity
that we incidentally observe between what we generally call crowd work \& gig work
and the historical practice of piecework and subsequent factory work
is more than passing;
that the phenomena researchers have observed in on--demand digitally mediated labor markets
were inevitable milestones in the birth and life of piecework.
We will set out to show that this perspective of crowd work as an embodiment of piecework
predicts the myriad outcomes of contemporary crowd work, including
our developments of work--flows further abstracting work,
the troubling effects of those developments on factors such as pay and work quality, and
many if not all of the frustrations researchers have discovered among workers
in the study of crowd and gig work.

``But'',
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor there is nothing new under the sun''
\cite{scholz2012digital}.
For one, information work
(e.g. Amazon Mechanical Turk (AMT) \& Upwork)
and digitally managed work in general make it substantially easier
to keep workers geographically dispersed
compared to the factory workers that followed home--based piecework.
This aspect of work renders workers virtually invisible to the task solicitors
--- or ``requesters'' ---
despite being significantly more connected than historical pieceworkers were % this is a weak point...
\cite{turkopticon}.
Secondly, while
factory foremen and other middle--men
traditionally mediated the relationships between workers and managers,
today the visible agents are \textit{systems};
rather than employing individuals who ``personified the functions of management''
and can thus negotiate workers' needs,
socio--technical systems mediate these interactions % often with unrewarding outcomes
\cite{wray1949marginal}.
% \cite{storiesIraniSilberman}.
Finally, this characteristic of modern piecework makes
worker coordination for collective advocacy and action significantly more difficult,
necessitating special consideration to maintain the inertia of collective will
while focusing that energy productively
\cite{dynamo}.
% \ali{I really don't like this paragraph\dots}
% here are undoubtedly more examples of differences.
% How do I not stake a claim that this is comprehensive?
% Or should I really flesh this out and make it (comprehensive)?

>>>>

\section{Introduction}
% \itshape 
\begin{itemize}
  \item on--demand labor has consumed an increasing proportion of the labor market in the past ten years [\textit{Pew research on on--demand labor}]
  \item the work surrounding this topic has ranged from Turk work processes to resisting Uber \& other gig labor platforms \cite{bernsteinSoylent,uberAlgorithm}
  \item some researchers have tackled understanding this new instantiation of work, but come up short.
  \item we offer a framing on this topic that situates the research so far on a timeline of the maturation of another form of work that emerged approximately 150 years ago
  --- that is, piecework --- which convincingly suggests that on--demand labor in the form of Turking, driving for Uber, etc\dots are in fact little more than piecework re--surging today.
  \item this paper will trace the body of research describing microwork --- and later gig work --- and place it in the context of historical piecework and the industrial revolution as a whole.
  \item informed by this new lens, we'll then turn our attention to the future of this re--emergent form of work, and suggest ways that researchers and users of on--demand labor might influence the outcomes we predict in this paper.
\end{itemize}

% The past decade has seen
% paid microtasking, the ``sharing economy'', and other instantiations of on--demand contract work
% grow to occupy the fascination of both academic circles and our culture as a whole
% \cite{Ross,CrowdsourcingUserStudies,scholz2012digital}.
% The research community has made connections between this emergent form of work
% and the historically situated ``piecework'',
% as well as a number of observations relating to
% the frustration workers feel stemming from the management of this work,
% but situating the causes of these frustrations either in the larger body of scholarship on crowd work,
% or crowd work itself,
% has proven difficult;
% the connection between crowd work and a historical parallel contextualizing its ongoing developments 
% hasn't been deeply made yet
% \cite{turkopticon,dynamo,uberAlgorithm}.

% While much of this work appears to gesture toward
% the parallels between contemporary on--demand work and piecework,
% it's proven difficult to bring the totality of these observations into focus using one theoretical lens.
% This paper will attempt to do so by arguing that
% the topics social computing researchers have investigated are
% not just parallel to historical piecework and
% the process of factorization that took place in the early \nth{20} century;
% indeed, these phenomena \textit{precipitate and reinforce each other}.

% In the reflection on the literature published in the last 5 years since
% \citeauthor{crowdworkFuture}'s 
% \citetitle{crowdworkFuture},
% we notice a broader trend describing the change in work that's being done
% \cite{crowdworkFuture}.
% Following the improvements in
% breaking down tasks,
% delegating work, and
% managing workers more broadly,
% crowd--powered work has continued to parallel historical piecework's trajectory
% by outgrowing ad--hoc worker groups and coalescing into more formal working groups,
% for example through the use of a ``white list'' of familiar workers.
% We might call this the regularization of factory work.

% Making sense of the broader field of crowd work
% by looking at the movements toward
% distributing work,
% routinizing and breaking down tasks,
% and externally managing workers
% as linked to one another, 
% we give ourselves a framing of contemporary piecework that explains,
% and arguably predicts,
% what we have seen thus far
% --- and perhaps what we should expect to see going forward.

% This paper will attempt to demonstrate that the familiarity
% that we incidentally observe between what we generally call crowd work \& gig work
% and the historical practice of piecework and subsequent factory work
% is more than passing;
% that the phenomena researchers have observed in on--demand digitally mediated labor markets
% were inevitable milestones in the birth and life of piecework.
% We will set out to show that this perspective of crowd work as an embodiment of piecework
% predicts the myriad outcomes of contemporary crowd work, including
% our developments of work--flows further abstracting work,
% the troubling effects of those developments on factors such as pay and work quality, and
% many if not all of the frustrations researchers have discovered among workers
% in the study of crowd and gig work.

% ``But'',
% as \citeauthor{scholz2012digital} points out,
% ``it would be wrong to conclude that
% in the realm of digital labor there is nothing new under the sun''
% \cite{scholz2012digital}.
% For one, information work
% (e.g. Amazon Mechanical Turk (AMT) \& Upwork)
% and digitally managed work in general make it substantially easier
% to keep workers geographically dispersed
% compared to the factory workers that followed home--based piecework.
% This aspect of work renders workers virtually invisible to the task solicitors
% --- or ``requesters'' ---
% despite being significantly more connected than historical pieceworkers were % this is a weak point...
% \cite{turkopticon}.
% Secondly, while
% factory foremen and other middle--men
% traditionally mediated the relationships between workers and managers,
% today the visible agents are \textit{systems};
% rather than employing individuals who ``personified the functions of management''
% and can thus negotiate workers' needs,
% socio--technical systems mediate these interactions % often with unrewarding outcomes
% \cite{wray1949marginal}.
% % \cite{storiesIraniSilberman}.
% Finally, this characteristic of modern piecework makes
% worker coordination for collective advocacy and action significantly more difficult,
% necessitating special consideration to maintain the inertia of collective will
% while focusing that energy productively
% \cite{dynamo}.
% % \ali{I really don't like this paragraph\dots}
% % here are undoubtedly more examples of differences.
% % How do I not stake a claim that this is comprehensive?
% % Or should I really flesh this out and make it (comprehensive)?
